\defjrnart{wucollateral}{Felix Wu, Collateral Censorship and the Limits of Intermediary Immunity, 87 Notre Dame Law Review 293 (2013)}

\defjrnart{citronwittes}
{
title={The Internet Will Not Break: Denying Bad Samaritans § 230 Immunity},
author={Danielle Keats Citron},
author={Benjamin Wittes},
date={2017},
volume=86,
page=401,
journal=Fordham Law Review
}


% economics of liability
% economic models of liability start from Brown and is further developed by many important contributions, including Shavell, which are summarized in Shavell

\defjrnart{brown1973toward}
{
  title={Toward an economic theory of liability},
  author={Brown, John Prather},
  journal={The Journal of Legal Studies},
  volume={2},
  number={2},
  pages={323--349},
  year={1973},
  publisher={The University of Chicago Law School}
}

\defjrnart{shavell1980strict}
{
  title={Strict liability versus negligence},
  author={Shavell, Steven},
  journal={The Journal of Legal Studies},
  volume={9},
  number={1},
  pages={1--25},
  year={1980},
  publisher={The University of Chicago Law School}
}

\defjrnart{shavell2009accident}
{
  title={Economic analysis of accident law},
  author={Shavell, Steven},
  year={2009},
  publisher={Harvard University Press}
}

% product liability, articles that study imperfect information about product risk

\defjrnart{polinsky2010uneasy}
{
  title={The uneasy case for product liability},
  author={Polinsky, A Mitchell and Shavell, Steven},
  journal={Harvard Law Review},
  pages={1437--1492},
  year={2010},
  publisher={JSTOR}
}

\defjrnart{hay2005manufacturer}
{
  title={Manufacturer liability for harms caused by consumers to others},
  author={Hay, Bruce and Spier, Kathryn E},
  journal={American Economic Review},
  volume={95},
  number={5},
  pages={1700--1711},
  year={2005},
  publisher={American Economic Association}
}

\defjrnart{daughety2013economic}
{
  title={Economic analysis of products liability: Theory},
  author={Daughety, Andrew F and Reinganum, Jennifer F},
  title={Research handbook on the economics of torts},
  pages={69--96},
  year={2013},
  publisher={Edward Elgar Publishing}
}

% intermediary liability

\defjrnart{hua2021holding}
{
  title={Holding platforms liable},
  author={Hua, Xinyu and Spier, Kathryn E},
  journal={HKUST Business School Research Paper},
  number={2021-048},
  year={2021}
}

\defjrnart{buiten2020rethinking}
{
  title={Rethinking liability rules for online hosting platforms},
  author={Buiten, Miriam C and De Streel, Alexandre and Peitz, and Martin},
  journal={International Journal of Law and Information Technology},
  volume={28},
  number={2},
  pages={139--166},
  year={2020},
  publisher={Oxford University Press}
}

\defjrnart{lefouili2022economics}
{
  title={The economics of platform liability},
  author={Lefouili, Yassine and Madio, Leonardo},
  journal={European Journal of Law and Economics},
  volume={53},
  number={3},
  pages={319--351},
  year={2022},
  publisher={Springer}
}

\defjrnart{lichtman2006holding}{
  title={Holding internet service providers accountable},
  author={Lichtman, Doug and Posner, Eric A},
  journal={Sup. Ct. Econ. Rev.},
  volume={14},
  pages={221},
  year={2006},
  publisher={HeinOnline}
}


%% Content Moderation

\defjrnart{grimmelmann2015virtues}
{
  title={The virtues of moderation},
  author={Grimmelmann, James},
  journal={Yale JL \& Tech.},
  volume={17},
  pages={42},
  year={2015},
  publisher={HeinOnline}
}


\defjrnart{evans2012governing}
{
  title={Governing bad behavior by users of multi-sided platforms},
  author={Evans, David S},
  journal={Berkeley Tech. LJ},
  volume={27},
  pages={1201},
  year={2012},
  publisher={HeinOnline}
}

\defjrnart{crawford2016flag}
{
  title={What is a flag for? Social media reporting tools and the vocabulary of complaint},
  author={Crawford, Kate and Gillespie, Tarleton},
  journal={New Media \& Society},
  volume={18},
  number={3},
  pages={410--428},
  year={2016},
  publisher={Sage Publications Sage UK: London, England}
}

\defjrnart{goldman2021content}
{
  title={Content Moderation Remedies},
  author={Goldman, Eric},
  journal={Mich. Tech. L. Rev.},
  volume={28},
  pages={1},
  year={2021},
  publisher={HeinOnline}
}

% economic model of moderation

\defjrnart{liu2022implications}
{
  title={Implications of revenue models and technology for content moderation strategies},
  author={Liu, Yi and Yildirim, Pinar and Zhang, Z John},
  journal={Marketing Science},
  year={2022},
  publisher={INFORMS}
}

% section 512, over-removal evidence

\defjrnart{urban2005takedown}
{
  title={Efficient process or chilling effects-takedown notices under Section 512 of the Digital Millennium Copyright Act},
  author={Urban, Jennifer M and Quilter, Laura},
  journal={Santa Clara Computer \& High Tech. LJ},
  volume={22},
  pages={621},
  year={2005},
  publisher={HeinOnline}
}


\defjrnart{urban2017everyday}
{
  title={Notice and takedown in everyday practice},
  author={Urban, Jennifer M and Karaganis, Joe and Schofield, Brianna},
  journal={UC Berkeley Public Law Research Paper},
  number={2755628},
  year={2017}
}

\defjrnart{seng2020copyrighting}
{
  title={Copyrighting copywrongs: An empirical analysis of errors with automated DMCA takedown notices},
  author={Seng, Daniel},
  journal={Santa Clara High Tech. LJ},
  volume={37},
  pages={119},
  year={2020},
  publisher={HeinOnline}
}

% section 230 
\defjrnart{byrd2019cda}{
  title={CDA 230 for a Smart Internet},
  author={Byrd, Madeline and Strandburg, Katherine J},
  journal={Fordham L. Rev.},
  volume={88},
  pages={405},
  year={2019},
  publisher={HeinOnline}
}

\defjrnart{reidenberg2012section}{
  title={Section 230 of the communications decency Act: A survey of the legal literature and reform proposals},
  author={Reidenberg, Joel R and Debelak, Jamela and Kovnot, Jordan and Miao, Tiffany},
  journal={Fordham Law School-Center on Law and Information Policy, Fordham Law Legal Studies Research Paper},
  number={2046230},
  year={2012}
}

\defbook{citron2014hate}{
  title={Hate crimes in cyberspace},
  author={Citron, Danielle Keats},
  year={2014},
  publisher={Harvard University Press}
}

\defjrnart{citron2009cyber}{
  title={Cyber civil rights},
  author={Citron, Danielle Keats},
  journal={BUL Rev.},
  volume={89},
  pages={61},
  year={2009},
  publisher={HeinOnline}
}

\defjrnart{citron2018problem}{
  title={The Problem Isn't Just Backpage: Revising Section 230 Immunity},
  author={Citron, Danielle K and Wittes, Benjamin},
  journal={Georgetown Law Technology Review},
  volume={2},
  number={2},
  pages={453},
  year={2018},
  publisher={Georgetown University Law Center}
}

\defjrnart{citron2020internet}{
  title={The internet as a speech machine and other myths confounding section 230 reform},
  author={Citron, Danielle Keats and Franks, Mary Anne},
  journal={U. Chi. Legal F.},
  pages={45},
  year={2020},
  publisher={HeinOnline}
}

\defjrnart{citron2022fix}{
  title={How To Fix Section 230},
  author={Citron, Danielle Keats},
  journal={Boston University Law Review, Forthcoming, Virginia Public Law and Legal Theory Research Paper},
  number={2022-18},
  year={2022}
}

\defjrnart{schruers2002history}{
  title={The history and economics of ISP liability for third party content},
  author={Schruers, Matthew},
  journal={Va. L. Rev.},
  volume={88},
  pages={205},
  year={2002},
  publisher={HeinOnline}
}


\defjrnart{reesesafeharbors}{
R. Anthony Reese, The Relationship Between the ISP Safe Harbors and the Ordinary Rules of Copyright Liability, 32 Columbia Journal of Law and the Arts 427 (2009)}
% 230 reform


\defcase{strattonoakmont}{
Stratton Oakmont, Inc. v. Prodigy Services Co., 23 Media L. Rep. 1794 (N.Y. Sup. Ct. 1995)
}

\defcase{zeran}{
Zeran v. America Online, Inc., 129 F. 3d 327 (4th Cir. 1997)
}

\defwebsite{kellerpact}{
 author={Daphne Keller},
 title={CDA 230 Reform Grows Up: The PACT Act Has Problems, But It’s Talking About the Right Things},
 journal={Stanford CIS Blog},
 date={July 16, 2020} }

\defwebsite{dsa}{
  title=Digital Services Act
}
% 230 vs First Amendment





% 230 vs 512



% US, EU



