%
% Court documents.
%
\hi@abbrev{Amicus Curiae}{Am. Cur.}
\hi@abbrev{Amici Curiae}{Am. Cur.}
\hi@abbrev{Admissions}{Admis.}
\hi@abbrev{Admission}{Admis.}
\hi@abbrev{Affidavits}{Affs.}
\hi@abbrev{Affidavit}{Aff.}
\hi@abbrev{Amended}{Am.}
\hi@abbrev{Appendices}{Apps.}
\hi@abbrev{Appendixes}{Apps.}
\hi@abbrev{Appendix}{App.}
\hi@abbrev{Attachment}{Attach.}
\hi@abbrev{Attorneys}{Att'ys}
\hi@abbrev{Attorney}{Att'y}
\hi@abbrev{Brief}{Br.}
\hi@abbrev{Certiorari}{Cert.}
\hi@abbrev{Complaint}{Compl.}
\hi@abbrev{Counterclaim}{Countercl.}
\hi@abbrev{Court}{Ct.}
\hi@abbrev{Cross-claim}{Cross-cl.}
\hi@abbrev{Declaration}{Decl.}
\hi@abbrev{Defendants'}{Defs.'}
\hi@abbrev{Defendants}{Defs.}
\hi@abbrev{Defendant's}{Def.'s}
\hi@abbrev{Defendant}{Def.}
\hi@abbrev{Demurrer}{Dem.}
\hi@abbrev{Denying}{Den.}
\hi@abbrev{Deposition}{Dep.}
\hi@abbrev{Discovery}{Disc.}
\hi@abbrev{Documents}{Docs.}
\hi@abbrev{Document}{Doc.}
\hi@abbrev{Exhibits}{Exs.}
\hi@abbrev{Exhibit}{Ex.}
\hi@abbrev{Hearings}{Hr'gs}
\hi@abbrev{Hearing}{Hr'g}
\hi@abbrev{Injunctions}{Injs.}
\hi@abbrev{Injunction}{Inj.}
\hi@abbrev{Interrogatories}{Interrogs.}
\hi@abbrev{Interrogatory}{Interrog.}
\hi@abbrev{Joint Appendix}{J.A.}
\hi@abbrev{Judgment}{J.}
\hi@abbrev{Memorandum}{Mem.}
\hi@abbrev{Minutes}{Mins.}
\hi@abbrev{Motions}{Mots.}
\hi@abbrev{Motion}{Mot.}
\hi@abbrev{Opinions}{Ops.}
\hi@abbrev{Opinion}{Op.}
\hi@abbrev{Oppositions}{Opp'ns}
\hi@abbrev{Opposition}{Opp'n}
\hi@abbrev{Petitioners}{Pet'rs}
\hi@abbrev{Petitioner}{Pet'r}
\hi@abbrev{Petitions}{Pets.}
\hi@abbrev{Petition}{Pet.}
\hi@abbrev{Plaintiffs'}{Pls.'}
\hi@abbrev{Plaintiffs}{Pls.}
\hi@abbrev{Plaintiff's}{Pl.'s}
\hi@abbrev{Plaintiff}{Pl.}
\hi@abbrev{Points and Authorities}{P. \& A.}
\hi@abbrev{Preliminary}{Prelim.}
\hi@abbrev{Production}{Produc.}
\hi@abbrev{Reconsideration}{Recons.}
\hi@abbrev{Record}{R.}
\hi@abbrev{Rehearing}{Reh'g}
\hi@abbrev{Reporter}{Rep.}
\hi@abbrev{Request}{Req.}
\hi@abbrev{Respondents}{Resp'ts}
\hi@abbrev{Respondent}{Resp't}
\hi@abbrev{Response}{Resp.}
\hi@abbrev{Summary}{Summ.}
\hi@abbrev{Support}{Supp.}
\hi@abbrev{Temporary Restraining Order}{TRO}
\hi@abbrev{Testimony}{Test.}
\hi@abbrev{Transcript}{Tr.}
\hi@abbrev{Verified Statement}{V.S.}
\hi@abbrev{and}{\&}
\hi@abbrev{Stipulation}{Stip.}
\hi@abbrev{The}{}
\hi@abbrev{the}{}
\hi@abbrev{A}{}
\hi@abbrev{a}{}
\hi@abbrev{An}{}
\hi@abbrev{an}{}
\hi@abbrev{of}{}
\hi@abbrev{for}{}
\hi@abbrev{from}{}
\hi@abbrev{in}{}
\hi@abbrev{to}{}
\hi@abbrev{at}{}
\hi@abbrev{by}{}
\hi@abbrev{on}{}
\hi@abbrev{over}{}
\hi@abbrev{per}{}
\hi@abbrev{with}{}
