%
% Subdivisions of books.
%
\hi@abbrev{addendum}{add. }{addenda}{adds. }
\hi@abbrev{amendment}{amend. }{amendments}{amends. }
\hi@abbrev{annotation}{annot. }{annotations}{annots. }
\hi@abbrev{appendix}{app. }{appendices}{apps. }
\hi@abbrev{annex}{annex }{annexes}{annexes }
\hi@abbrev{article}{art. }{articles}{arts. }
\hi@abbrev{Article}{Art. }{Articles}{Arts. } % For US Constitution
\hi@abbrev{bibliography}{bibliog. }{bibliographies}{bibliogs. }
\hi@abbrev{book}{bk. }{books}{bks. }
\hi@abbrev{chapter}{ch. }{chapters}{chs. }
\hi@abbrev{clause}{cl. }{clauses}{cls. }
\hi@abbrev{column}{col. }{columns}{cols. }
\hi@abbrev{commentary}{cmt. }{commentaries}{cmts. }
\hi@abbrev{comment}{cmt. }{comments}{cmts. }
\hi@abbrev{decision}{dec. }{decisions}{decs. }
\hi@abbrev{example}{ex. }{examples}{exs. }
\hi@abbrev{Exhibit}{Exh. }{Exhibits}{Exhs. }
\hi@abbrev{figure}{fig.}{figures}{figs.}
\hi@abbrev{folio}{fol. }{folios}{fols. }
\hi@abbrev{historical-note}{hist. n.}{historical-notes}{hist. nn.}
\hi@abbrev{hypothetical}{hypo. }{hypotheticals}{hypos. }
\hi@abbrev{illustration}{illus. }{illustrations}{illus. }
\hi@abbrev{introduction}{intro. }{introductions}{intros. }
\hi@abbrev{line}{l. }{lines}{ll. }
\hi@abbrev{note}{n.}{notes}{nn.}
\hi@abbrev{number}{No. }{numbers}{Nos. }
\hi@abbrev{paragraph}{para. }{paragraphs}{paras. }
\hi@abbrev{part}{pt. }{parts}{pts. }
\hi@abbrev{preamble}{pmbl. }{preambles}{pmbls. }
\hi@abbrev{principle}{princ. }{principles}{princs. }
\hi@abbrev{publication}{pub. }{publications}{pubs. }
\hi@abbrev{rule}{R. }{rules}{R. }
\hi@abbrev{schedule}{sched. }{schedules}{scheds. }
\hi@abbrev{section}{sec. }{sections}{secs. }
\hi@abbrev{series}{ser. }{series}{ser. }
\hi@abbrev{serial}{ser. }{serials}{ser. }
\hi@abbrev{subdivision}{subdiv. }{subdivisions}{subdivs. }
\hi@abbrev{subsection}{subsec. }{subsections}{subsecs. }
\hi@abbrev{subtitle}{subtit. }{subtitles}{subtits. }
\hi@abbrev{table}{tbl.}{tables}{tbls.}
\hi@abbrev{title}{tit. }{titles}{tits. }
\hi@abbrev{volume}{vol. }{volumes}{vols. }
%
% Adding abbreviation for claim
%
\hi@abbrev{claim}{cl. }{claims}{cls. }
\endinput
