%
% Non-institutional title words in journal names.
% Institutional words are contained in the file hitbl13a.
% Full journal abbreviations are contained in hitbl13b.
%
% In the 20th Edition this refers to Table T13.2.
%
%
\hi@abbrev{Academic}{Acad.}
\hi@abbrev{Accountancy}{Acct.}
\hi@abbrev{Accountants}{Acct.}
\hi@abbrev{Accountant}{Acct.}
\hi@abbrev{Accounting}{Acct.}
\hi@abbrev{Account}{Acct.}
\hi@abbrev{Administration}{Admin.}
\hi@abbrev{Administrative}{Admin.}
\hi@abbrev{Administrator}{Admin.}
\hi@abbrev{Advertising}{Advert.}
\hi@abbrev{Advocacy}{Advoc.}
\hi@abbrev{Advocate}{Advoc.}
\hi@abbrev{Affairs}{Aff.}
\hi@abbrev{African}{Afr.}
\hi@abbrev{Africa}{Afr.}
\hi@abbrev{Agricultural}{Agric.}
\hi@abbrev{Agriculture}{Agric.}
\hi@abbrev{Amendment}{Amend.}
\hi@abbrev{American Law Reports}{A\abb@dot L\abb@dot R\abb@dot}
\hi@abbrev{Americas}{Am.}
\hi@abbrev{American}{Am.}
\hi@abbrev{America}{Am.}
\hi@abbrev{Annual}{Ann.}
\hi@abbrev{Appellate}{App.}
\hi@abbrev{Arbitration}{Arb.}
\hi@abbrev{Arbitrators}{Arb.}
\hi@abbrev{Association}{Ass'n}
\hi@abbrev{Attorneys}{Att'ys}
\hi@abbrev{Attorney}{Att'y}
\hi@abbrev{Bankruptcy}{Bankr.}
\hi@abbrev{Bar}{B\abb@dot}
\hi@abbrev{Behavioral}{Behav.}
\hi@abbrev{Behavior}{Behav.}
\hi@abbrev{British}{Brit.}
\hi@abbrev{Bulletin}{Bull.}
\hi@abbrev{Business}{Bus.}
\hi@abbrev{Capital}{Cap.}
\hi@abbrev{Catholic}{Cath.}
\hi@abbrev{Children's}{Child.}
\hi@abbrev{Children}{Child.}
\hi@abbrev{Chronicle}{Chron.}
\hi@abbrev{Circuit}{Cir.}
\hi@abbrev{Civil Liberty}{C\abb@dot L\abb@dot }
\hi@abbrev{Civil Liberties}{C\abb@dot L\abb@dot }
\hi@abbrev{Civil Rights}{C\abb@dot R\abb@dot }
\hi@abbrev{Civil}{Civ.}
\hi@abbrev{Commentary}{Comment.}
\hi@abbrev{Communications}{Comm.}
\hi@abbrev{Communication}{Comm.}
\hi@abbrev{Comparative}{Comp.}
\hi@abbrev{Conference}{Conf.}
\hi@abbrev{Congressional}{Cong.}
\hi@abbrev{Constitutional}{Const.}
\hi@abbrev{Constitution}{Const.}
\hi@abbrev{Contemporary}{Contemp.}
\hi@abbrev{Contracts}{Cont.}
\hi@abbrev{Contract}{Cont.}
\hi@abbrev{Conveyancer}{Conv.}
\hi@abbrev{Corporate}{Corp.}
\hi@abbrev{Corporation}{Corp.}
\hi@abbrev{Cosmetic}{Cosm.}
\hi@abbrev{Counselors}{Couns.}
\hi@abbrev{Counselor's}{Couns.}
\hi@abbrev{Counselor}{Couns.}
\hi@abbrev{Counsel}{Couns.}
\hi@abbrev{Criminal}{Crim.}
\hi@abbrev{Defense}{Def.}
\hi@abbrev{Delinquency}{Delinq.}
\hi@abbrev{Derecho}{Der.}
\hi@abbrev{Developments}{Dev.}
\hi@abbrev{Development}{Dev.}
\hi@abbrev{Digest}{Dig.}
\hi@abbrev{Diplomacy}{Dipl.}
\hi@abbrev{Dispute}{Disp.}
\hi@abbrev{Doctor}{Dr.}
\hi@abbrev{Economically}{Econ.}
\hi@abbrev{Economical}{Econ.}
\hi@abbrev{Economics}{Econ.}
\hi@abbrev{Economic}{Econ.}
\hi@abbrev{Economy}{Econ.}
\hi@abbrev{Educational}{Educ.}
\hi@abbrev{Education}{Educ.}
\hi@abbrev{Employee}{Emp.}
\hi@abbrev{Employment}{Emp.}
\hi@abbrev{English}{Eng.}
\hi@abbrev{Entertainment}{Ent.}
\hi@abbrev{Environmental}{Envtl.}
\hi@abbrev{Environment}{Env't}
\hi@abbrev{Estates}{Est.}
\hi@abbrev{Estate}{Est.}
\hi@abbrev{European}{Eur.}
\hi@abbrev{Europe}{Eur.}
\hi@abbrev{Faculty}{Fac.}
\hi@abbrev{Family}{Fam.}
\hi@abbrev{Federal}{Fed.}
\hi@abbrev{Federation}{Fed'n}
\hi@abbrev{Finance}{Fin.}
\hi@abbrev{Financial}{Fin.}
\hi@abbrev{Fortnightly}{Fort.}
\hi@abbrev{Forum}{F\abb@dot }
\hi@abbrev{Foundations}{Found.}
\hi@abbrev{Foundation}{Found.}
\hi@abbrev{General}{Gen.}
\hi@abbrev{Government}{Gov't}
\hi@abbrev{Hispanic}{Hisp.}
\hi@abbrev{Historical}{Hist.}
\hi@abbrev{History}{Hist.}
\hi@abbrev{Hospital}{Hosp.}
\hi@abbrev{Human}{Hum.}
\hi@abbrev{Humanity}{Human.}
\hi@abbrev{Humanities}{Human.}
\hi@abbrev{Immigration}{Immigr.}
\hi@abbrev{Independent}{Indep.}
\hi@abbrev{Industrial}{Indus.}
\hi@abbrev{Information}{Info.}
\hi@abbrev{Injury}{Inj.}
\hi@abbrev{Insurance}{Ins.}
\hi@abbrev{Intellectual}{Intell.}
\hi@abbrev{Interdisciplinary}{Interdisc.}
\hi@abbrev{Interest}{Int.}
\hi@abbrev{International}{Int'l}
\hi@abbrev{Investments}{Inv.}
\hi@abbrev{Investors}{Inv.}
\hi@abbrev{Journal}{J\abb@dot }
\hi@abbrev{Judicial}{Jud.}
\hi@abbrev{Juridical}{Jurid.}
\hi@abbrev{Jurisprudence}{Juris.}
\hi@abbrev{Justice}{Just.}
\hi@abbrev{Juvenile}{Juv.}
\hi@abbrev{Labor}{Lab.}
\hi@abbrev{Labour}{Lab.}
\hi@abbrev{Law}{L\abb@dot }
\hi@abbrev{Lawyers'}{Law.}
\hi@abbrev{Lawyers}{Law.}
\hi@abbrev{Lawyer's}{Law.}
\hi@abbrev{Lawyer}{Law.}
\hi@abbrev{Legislation}{Legis.}
\hi@abbrev{Legislative}{Legis.}
\hi@abbrev{Library}{Libr.}
\hi@abbrev{Librarian}{Libr.}
\hi@abbrev{Libraries}{Libr.}
\hi@abbrev{Litigation}{Litig.}
\hi@abbrev{Local}{Loc.}
\hi@abbrev{Magazine}{Mag.}
\hi@abbrev{Management}{Mgmt.}
\hi@abbrev{Maritime}{Mar.}
\hi@abbrev{Market}{Mkt.}
\hi@abbrev{Matrimonial}{Matrim.}
\hi@abbrev{Medical}{Med.}
\hi@abbrev{Medicine}{Med.}
\hi@abbrev{Military}{Mil.}
\hi@abbrev{Mineral}{Min.}
\hi@abbrev{Modern}{Mod.}
\hi@abbrev{Municipal}{Mun.}
\hi@abbrev{National}{Nat'l}
\hi@abbrev{Nationality}{Nat'lity}
\hi@abbrev{Natural}{Nat.}
\hi@abbrev{Negligence}{Negl.}
\hi@abbrev{Negotiation}{Negot.}
\hi@abbrev{new series}{n.s.}
\hi@abbrev{Newsletter}{Newsl.}
\hi@abbrev{Office}{Off.}
\hi@abbrev{Order}{Ord.}
\hi@abbrev{Organization}{Org.}
\hi@abbrev{Patent}{Pat.}
\hi@abbrev{Personal}{Pers.}
\hi@abbrev{Perspectives}{Persp.}
\hi@abbrev{Perspective}{Persp.}
\hi@abbrev{Philosophy}{Phil.}
\hi@abbrev{Philosophical}{Phil.}
\hi@abbrev{Planning}{Plan.}
\hi@abbrev{Policy}{Pol'y}
\hi@abbrev{Political}{Pol.}
\hi@abbrev{Politics}{Pol.}
\hi@abbrev{Practical}{Prac.}
\hi@abbrev{Practice}{Prac.}
\hi@abbrev{Practitioners}{Prac.}
\hi@abbrev{Practitioner}{Prac.}
\hi@abbrev{Private}{Priv.}
\hi@abbrev{Probate}{Prob.}
\hi@abbrev{Probation}{Prob.}
\hi@abbrev{Problems}{Probs.}
\hi@abbrev{Proceedings}{Proc.}
\hi@abbrev{Procedure}{Proc.}
\hi@abbrev{Products Liability}{Prod. Liab.}
\hi@abbrev{Professional}{Prof.}
\hi@abbrev{Profession}{Prof.}
\hi@abbrev{Property}{Prop.}
\hi@abbrev{Psychology}{Psychol.}
\hi@abbrev{Psychological}{Psychol.}
\hi@abbrev{Public}{Pub.}
\hi@abbrev{Publishing}{Pub.}
\hi@abbrev{Quarterly}{Q\abb@dot }
\hi@abbrev{Record}{Rec.}
\hi@abbrev{Referees}{Ref.}
\hi@abbrev{Referee}{Ref.}
\hi@abbrev{Register}{Reg.}
\hi@abbrev{Regulation}{Reg.}
\hi@abbrev{Regulatory}{Reg.}
\hi@abbrev{Relations}{Rel.}
\hi@abbrev{Reporter}{Rep.}
\hi@abbrev{Reports}{Rep.}
\hi@abbrev{Report}{Rep.}
\hi@abbrev{Reproduction}{Reprod.}
\hi@abbrev{Reproductive}{Reprod.}
\hi@abbrev{Research}{Res.}
\hi@abbrev{Reserve}{Res.}
\hi@abbrev{Resolution}{Resol.}
\hi@abbrev{Responsibility}{Resp.}
\hi@abbrev{Review}{Rev.}
\hi@abbrev{Revista}{Rev.}
\hi@abbrev{Rights}{Rts.}
\hi@abbrev{Sciences}{Sci.}
\hi@abbrev{Science}{Sci.}
\hi@abbrev{Scientific}{Sci.}
\hi@abbrev{Scottish}{Scot.}
\hi@abbrev{Section}{Sec.}
\hi@abbrev{Securities}{Sec.}
\hi@abbrev{Sentencing}{Sent'g}
\hi@abbrev{Service}{Serv.}
\hi@abbrev{Social}{Soc.}
\hi@abbrev{Society}{Soc'y}
\hi@abbrev{Sociological}{Soc.}
\hi@abbrev{Sociology}{Soc.}
\hi@abbrev{Solicitors'}{Solic.}
\hi@abbrev{Solicitor's}{Solic.}
\hi@abbrev{Solicitors}{Solic.}
\hi@abbrev{Solicitor}{Solic.}
\hi@abbrev{Statistics}{Stat.}
\hi@abbrev{Statistical}{Stat.}
\hi@abbrev{Studies}{Stud.}
\hi@abbrev{Supreme Court}{Sup. Ct.}
\hi@abbrev{Survey}{Surv.}
\hi@abbrev{Symposium}{Symp.}
\hi@abbrev{System}{Sys.}
\hi@abbrev{Taxation}{Tax'n}
\hi@abbrev{Teachers}{Tchrs.}
\hi@abbrev{Teacher}{Tchr.}
\hi@abbrev{Technique}{Tech.}
\hi@abbrev{Technology}{Tech.}
\hi@abbrev{Telecommunications}{Telecomm.}
\hi@abbrev{Transnational}{Transnat'l}
\hi@abbrev{Transportation}{Transp.}
\hi@abbrev{Tribune}{Trib.}
\hi@abbrev{Trustee}{Tr.}
\hi@abbrev{Trusts}{Tr.}
\hi@abbrev{Trust}{Tr.}
\hi@abbrev{Urban}{Urb.}
\hi@abbrev{Uniform Commcercial Code}{UCC}
\hi@abbrev{Urban}{Urb.}
\hi@abbrev{Utility}{Util.}
\hi@abbrev{Utilities}{Util.}
\hi@abbrev{Weekly}{Wkly.}
\hi@abbrev{Week}{Wk.}
\hi@abbrev{Yearbook}{Y\abb@dot B\abb@dot }
\hi@abbrev{Year Book}{Y\abb@dot B\abb@dot }
%
% Inferred abbreviations
%
\ifnum\hi@jrnabb@inferlvl>\@ne
    \hi@abbrev{Atomic}{Atom.}
    \hi@abbrev{Cases}{Cas.}
    \hi@abbrev{Department}{Dep't}
    \hi@abbrev{Inequality}{Ineq.}
    \hi@abbrev{Investment}{Inv.}
    \hi@abbrev{Investor}{Inv.}
    \hi@abbrev{Liabilities}{Liab.}
    \hi@abbrev{Liability}{Liab.}
    \hi@abbrev{Nationalities}{Nat'lities}
    \hi@abbrev{Negotiations}{Negot.}
    \hi@abbrev{Products}{Prod.}
    \hi@abbrev{Juridica}{Jur.}
    \hi@abbrev{Technologies}{Techs.}
\fi
% Not exactly sure why these have to come at this point
\hi@abbrev{Courts}{Cts.}
\hi@abbrev{Court}{Ct.}
\hi@abbrev{Commerce}{Com.}
\hi@abbrev{Commercial}{Com.}
\hi@abbrev{and}{\&}
\endinput
