%
% Journal title abbreviations for institutional and geographic terms.
%
\hi@abbrev{American Society of Composers, Authors and Publishers}{ASCAP}
\hi@abbrev{Adelaide}{Adel.}
\hi@abbrev{Air Force}{A.F.}
\hi@abbrev{Albany}{Alb.}
\hi@abbrev{Boston College}{B.C.}
\hi@abbrev{Boston University}{B.U.}
\hi@abbrev{Buffalo}{Buff.}
\hi@abbrev{Brigham Young University}{BYU}
\hi@abbrev{Brooklyn}{Brook.}
\hi@abbrev{Capital University}{Cap. U.}
\hi@abbrev{Catholic University}{Cath. U.}
\hi@abbrev{Chapman}{Chap.}
\hi@abbrev{Cleveland}{Clev.}
\hi@abbrev{Columbia}{Colum.}
\hi@abbrev{Cumberland}{Cumb.}
\hi@abbrev{Denver}{Denv.}
\hi@abbrev{Dickinson}{Dick.}
\hi@abbrev{University of the D.C. David Clarke School of Law}{UDC/DCSL}
\hi@abbrev{Duquesne}{Duq.}
\hi@abbrev{Federal Circuit}{Fed. Cir.}
\hi@abbrev{Foreign Broadcast Information Service}{F.B.I.S.}
\hi@abbrev{George Mason}{Geo. Mason}
\hi@abbrev{George Washington}{Geo. Wash.}
\hi@abbrev{Georgetown}{Geo.}
\hi@abbrev{Gonzaga}{Gonz.}
\hi@abbrev{Harvard}{Harv.}
\hi@abbrev{Houston}{Hous.}
\hi@abbrev{John Marshall}{J. Marshall}
\hi@abbrev{Loyola}{Loy.}
\hi@abbrev{Marquette}{Marq.}
\hi@abbrev{Melbourne}{Melb.}
\hi@abbrev{University of Memphis}{U. Mem.}
\hi@abbrev{Northwestern}{Nw.}
\hi@abbrev{Pepperdine}{Pepp.}
\hi@abbrev{Pittsburgh}{Pitt.}
\hi@abbrev{Richmond}{Rich.}
\hi@abbrev{Rocky Mountain}{Rocky Mtn.}
\hi@abbrev{Rutgers-Camden}{Rutgers-Cam.}
\hi@abbrev{Saint}{St.}
\hi@abbrev{Saint Louis}{St. Louis}
\hi@abbrev{San Fernando Valley}{San Fern. V.}
\hi@abbrev{Southern Methodist University}{SMU}
\hi@abbrev{Southwestern}{Sw.}
\hi@abbrev{Stanford}{Stan.}
\hi@abbrev{Temple}{Temp.}
\hi@abbrev{Thomas Jefferson}{T. Jefferson}
\hi@abbrev{Thomas M. Cooley}{T.M. Cooley}
\hi@abbrev{Thurgood Marshall}{T. Marshall}
\hi@abbrev{Tulane}{Tul.}
\hi@abbrev{Vanderbilt}{Vand.}
\hi@abbrev{Valparaiso}{Val.}
\hi@abbrev{Villanova}{Vill.}
\hi@abbrev{Wall Street}{Wall St.}
\hi@abbrev{William and Mary}{Wm. and Mary} % Ampersand will be added later
\hi@abbrev{William Mitchell}{Wm. Mitchell}
\hi@abbrev{University of Cincinnati}{U. Cin.}
\hi@abbrev{University of California}{U.C.}
\hi@abbrev{University of Cal.}{U.C.}
\hi@abbrev{University of West Los Angeles}{UWLA}
\hi@abbrev{University of West L.A.}{UWLA}
\hi@abbrev{University of Toledo}{U. Tol.}
\hi@abbrev{University of Detroit}{U. Det.}
\hi@abbrev{Puertorriqueno}{P.R.}
\hi@abbrev{Universidad}{U.}
\hi@abbrev{Capital}{Cap.}
\hi@abbrev{George}{Geo.}
\hi@abbrev{William}{Wm.}
\hi@abbrev{Toledo}{Tol.}
\hi@abbrev{Academy}{Acad.}
\hi@abbrev{A.B.A.}{A.B.A.}
\hi@abbrev{ABA}{A.B.A.}
\hi@abbrev{American Bar Association}{A.B.A.}
\hi@abbrev{American Law Institute}{A.L.I.}
\hi@abbrev{Central}{Cent.}
\hi@abbrev{Center}{Ctr.}
\hi@abbrev{Centre}{Ctr.}
\hi@abbrev{Chartered Life Underwriters}{C.L.U.}
\hi@abbrev{College}{C.}
\hi@abbrev{East}{E.}
\hi@abbrev{Eastern}{E.}
\hi@abbrev{Institute}{Inst.}
\hi@abbrev{Law School}{L. Sch.} % To ensure the "Law" is part of institution
\hi@abbrev{North}{N.}
\hi@abbrev{Northern}{N.}
\hi@abbrev{Pacific}{Pac.}
\hi@abbrev{Puertorriqueno}{P.R.}
\hi@abbrev{School}{Sch.}
\hi@abbrev{Southern}{S.}
\hi@abbrev{South}{S.}
\hi@abbrev{State}{St.}
\hi@abbrev{United States}{U.S.}
\hi@abbrev{University}{U.}
\hi@abbrev{Universities}{U.}
\hi@abbrev{West}{W.}
\hi@abbrev{Western}{W.}
