%
% This file contains abbreviations for full journal titles.
%
%
\hi@abbrev{A.B.A. Journal}{A.B.A. J.}
\hi@abbrev{ABA Journal}{A.B.A. J.}
\hi@abbrev{Adelaide Law Review}{Adel. L. Rev.}
\hi@abbrev{Administrative Law Journal}{Admin. L.J.}
\hi@abbrev{Administrative Law Journal of American University}{Admin. L.J. Am. U.}
\hi@abbrev{Administrative Law Review}{Admin. L. Rev.}
\hi@abbrev{African-American Law and Policy Report}{Afr.-Am. L. \& Pol'y Rep.}
\hi@abbrev{Air Force Law Review}{A.F. L. Rev.}
\hi@abbrev{Akron Law Review}{Akron L. Rev.}
\hi@abbrev{Akron Tax Journal}{Akron Tax J.}
\hi@abbrev{Alabama Law Review}{Ala. L. Rev.}
\hi@abbrev{Alaska Law Review}{Alaska L. Rev.}
\hi@abbrev{Albany Law Journal of Science and Technology}{Alb. L.J. Sci. \& Tech.}
\hi@abbrev{Albany Law Review}{Alb. L. Rev.}
\hi@abbrev{American Bar Association Journal}{A.B.A. J.}
\hi@abbrev{American Review of International Arbitration}{Am. Rev. Int'l Arb.}
\hi@abbrev{American University International Law Review}{Am. U. Int'l L. Rev.}
\hi@abbrev{American University Journal of Gender, Social Policy and the Law}{Am. U. J. Gender Soc. Pol'y \& L.}
\hi@abbrev{American University Law Review}{Am. U. L. Rev.}
\hi@abbrev{Anglo-American Law Review}{Anglo-Am. L. Rev.}
\hi@abbrev{Animal Law}{Animal L.}
\hi@abbrev{Annals of the American Academy of Political and Social Science}{Annals Am. Acad. Pol. \& Soc. Sci.}
\hi@abbrev{Annals of Health Law}{Annals Health L.}
\hi@abbrev{Annual Review of Banking Law}{Ann. Rev. Banking L.}
\hi@abbrev{Annual Survey of American Law}{Ann. Surv. Am. L.}
\hi@abbrev{Annual Survey of International and Comparative Law}{Ann. Surv. Int'l \& Comp. L.}
\hi@abbrev{Arizona Journal of International and Comparative Law}{Ariz. J. Int'l \& Comp. L.}
\hi@abbrev{Arizona Law Review}{Ariz. L. Rev.}
\hi@abbrev{Arizona State Law Journal}{Ariz. St. L.J.}
\hi@abbrev{Arkansas Law Notes}{Ark. L. Notes}
\hi@abbrev{Arkansas Law Review}{Ark. L. Rev.}
\hi@abbrev{Army Lawyer}{Army Law.}
\hi@abbrev{Asian Law Journal}{Asian L.J.}
\hi@abbrev{Asian Pacific American Law Journal}{Asian Pac. Am. L.J.}
\hi@abbrev{Asian-Pacific Law and Policy Journal}{Asian-Pac. L. \& Pol'y J.}
\hi@abbrev{Atomic Energy Law Journal}{Atom. Energy L.J.}
\hi@abbrev{Auckland University Law Review}{Auckland U. L. Rev.}
\hi@abbrev{Banking Law Journal}{Banking L.J.}
\hi@abbrev{Bankruptcy Developments Journal}{Bankr. Dev. J.}
\hi@abbrev{Baylor Law Review}{Baylor L. Rev.}
\hi@abbrev{Behavioral Sciences and the Law}{Behav. Sci. \& L.}
\hi@abbrev{Berkeley Journal of Employment and Labor Law}{Berkeley J. Emp. \& Lab. L.}
\hi@abbrev{Berkeley Journal of Health Care Law}{Berkeley J. Health Care L.}
\hi@abbrev{Berkeley Journal of International Law}{Berkeley J. Int'l L.}
\hi@abbrev{Berkeley Technology Law Journal}{Berkeley Tech. L.J.}
\hi@abbrev{Berkeley Women's Law Journal}{Berkeley Women's L.J.}
\hi@abbrev{Black Law Journal}{Black L.J.}
\hi@abbrev{Boston College Environmental Affairs Law Review}{B.C. Envtl. Aff. L. Rev.}
\hi@abbrev{Boston College International and Comparative Law Review}{B.C. Int'l \& Comp. L. Rev.}
\hi@abbrev{Boston College Law Review}{B.C. L. Rev.}
\hi@abbrev{Boston College Third World Law Journal}{B.C. Third World L.J.}
\hi@abbrev{Boston University International Law Journal}{B.U. Int'l L.J.}
\hi@abbrev{Boston University Journal of Science and Technology Law}{B.U. J. Sci. \& Tech. L.}
\hi@abbrev{Boston University Journal of Tax Law}{B.U. J. Tax L.}
\hi@abbrev{Boston University Law Review}{B.U. L. Rev.}
\hi@abbrev{Boston University Public Interest Law Journal}{B.U. Pub. Int. L.J.}
\hi@abbrev{Brandeis Law Journal}{Brandeis L.J.}
\hi@abbrev{Brigham Young University Education and Law Journal}{BYU Educ. \& L.J.}
\hi@abbrev{Brigham Young University Journal of Public Law}{BYU J. Pub. L.}
\hi@abbrev{Brigham Young University Law Review}{BYU L. Rev.}
\hi@abbrev{Brooklyn Journal of International Law}{Brook. J. Int'l L.}
\hi@abbrev{Brooklyn Law Review}{Brook. L. Rev.}
\hi@abbrev{Buffalo Criminal Law Review}{Buff. Crim. L. Rev.}
\hi@abbrev{Buffalo Environmental Law Journal}{Buff. Envtl. L.J.}
\hi@abbrev{Buffalo Human Rights Law Review}{Buff. Hum. Rts. L. Rev.}
\hi@abbrev{Buffalo Law Review}{Buff. L. Rev.}
\hi@abbrev{Buffalo Public Interest Law Journal}{Buff. Pub. Int. L.J.}
\hi@abbrev{Buffalo Women's Law Journal}{Buff. Women's L.J.}
\hi@abbrev{Business Law Journal}{Bus. L.J.}
\hi@abbrev{Business Lawyer}{Bus. Law.}
\hi@abbrev{Business Week}{Bus. Wk.}
\hi@abbrev{California Bankruptcy Journal}{Cal. Bankr. J.}
\hi@abbrev{California Criminal Law Review}{Cal. Crim. L. Rev.}
\hi@abbrev{California Law Review}{Cal. L. Rev.}
\hi@abbrev{California Regulatory Law Reporter}{Cal. Reg. L. Rep.}
\hi@abbrev{California State Bar Journal}{Cal. St. B.J.}
\hi@abbrev{California Western International Law Journal}{Cal. W. Int'l L.J.}
\hi@abbrev{California Western Law Review}{Cal. W. L. Rev.}
\hi@abbrev{Cambridge Law Journal}{Cambridge L.J.}
\hi@abbrev{Campbell Law Review}{Campbell L. Rev.}
\hi@abbrev{Canada-United States Law Journal}{Can.-U.S. L.J.}
\hi@abbrev{Capital Defense Digest}{Cap. Def. Dig.}
\hi@abbrev{Capital University Law Review}{Cap. U. L. Rev.}
\hi@abbrev{Cardozo Arts and Entertainment Law Journal}{Cardozo Arts \& Ent. L.J.}
\hi@abbrev{Cardozo Law Review}{Cardozo L. Rev.}
\hi@abbrev{Cardozo Online Journal of Conflict Resolution}{Cardozo Online J. Conflict Resol.}
\hi@abbrev{Cardozo Women's Law Journal}{Cardozo Women's L.J.}
\hi@abbrev{Case and Comment}{Case \& Comment}
\hi@abbrev{Case Western Reserve Journal of International Law}{Case W. Res. J. Int'l L.}
\hi@abbrev{Case Western Reserve Law Review}{Case W. Res. L. Rev.}
\hi@abbrev{Catholic Lawyer}{Cath. Law.}
\hi@abbrev{Catholic University Law Review}{Cath. U. L. Rev.}
\hi@abbrev{Chapman Law Review}{Chap. L. Rev.}
\hi@abbrev{Chicago Tribune}{Chi. Trib.}
\hi@abbrev{Chicago-Kent Law Review}{Chi.-Kent L. Rev.}
\hi@abbrev{Chicano Law Review}{Chicano L. Rev.}
\hi@abbrev{Children's Legal Rights Journal}{Child. Legal Rts. J.}
\hi@abbrev{Clearinghouse Review}{Clearinghouse Rev.}
\hi@abbrev{Cleveland State Law Review}{Clev. St. L. Rev.}
\hi@abbrev{Cleveland-Marshall Law Review}{Clev.-Marshall L. Rev.}
\hi@abbrev{Clinical Law Review}{Clinical L. Rev.}
\hi@abbrev{Colorado Journal of International Environmental Law and Policy}{Colo. J. Int'l Envtl. L. \& Pol'y}
\hi@abbrev{Colorado Lawyer}{Colo. Law.}
\hi@abbrev{Columbia Business Law Review }{Colum. Bus. L. Rev.}
\hi@abbrev{Columbia Human Rights Law Review}{Colum. Hum. Rts. L. Rev.}
\hi@abbrev{Columbia Journal of Asian Law}{Colum. J. Asian L.}
\hi@abbrev{Columbia Journal of East European Law}{Colum. J. E. Eur. L.}
\hi@abbrev{Columbia Journal of Environmental Law}{Colum. J. Envtl. L.}
\hi@abbrev{Columbia Journal of European Law}{Colum. J. Eur. L.}
\hi@abbrev{Columbia Journal of Gender and Law}{Colum. J. Gender \& L.}
\hi@abbrev{Columbia Journal of Law and Social Problems}{Colum. J.L. \& Soc. Probs.}
\hi@abbrev{Columbia Journal of Transnational Law}{Colum. J. Transnat'l L.}
\hi@abbrev{Columbia Law Review}{Colum. L. Rev.}
\hi@abbrev{Columbia Science and Technology Law Review}{Colum. Sci. \& Tech. L. Rev.}
\hi@abbrev{Columbia-VLA Journal of Law and the Arts}{Colum.-VLA J.L. \& Arts}
\hi@abbrev{Common Market Law Review}{Common Mkt. L. Rev.}
\hi@abbrev{Comparative Labor Law Journal}{Comp. Lab. L.J.}
\hi@abbrev{Comparative Labor Law and Policy Journal}{Comp. Lab. L. \& Pol'y J.}
\hi@abbrev{Computer/Law Journal}{Computer/L.J.}
\hi@abbrev{Connecticut Journal of International Law}{Conn. J. Int'l L.}
\hi@abbrev{Connecticut Law Review}{Conn. L. Rev.}
\hi@abbrev{Connecticut Probate Law Journal}{Conn. Prob. L.J.}
\hi@abbrev{Conveyancer and Property Lawyer (new series)}{Conv. \& Prop. Law. (n.s.)}
\hi@abbrev{Cooley Law Review}{Cooley L. Rev.}
\hi@abbrev{Copyright Law Symposium (American Society of Composers, Authors and Publishers)}{Copyright L. Symp. (ASCAP)}
\hi@abbrev{Copyright Law Symposium}{Copyright L. Symp. (ASCAP)}
\hi@abbrev{Cornell International Law Journal}{Cornell Int'l L.J.}
\hi@abbrev{Cornell Journal of Law and Public Policy}{Cornell J.L. \& Pub. Pol'y}
\hi@abbrev{Cornell Law Review}{Cornell L. Rev.}
\hi@abbrev{Creighton Law Review}{Creighton L. Rev.}
\hi@abbrev{Criminal Law Forum}{Crim. L.F.}
\hi@abbrev{Criminal Law Review}{Crim. L. Rev.}
\hi@abbrev{Cumberland Law Review}{Cumb. L. Rev.}
\hi@abbrev{Current Medicine for Attorneys}{Current Med. for Att'ys}
\hi@abbrev{Currents: The International Trade Law Journal}{Currents: Int'l Trade L.J.}
\hi@abbrev{Dalhousie Law Journal}{Dalhousie L.J.}
\hi@abbrev{DePaul Business Law Journal}{DePaul Bus. L.J.}
\hi@abbrev{DePaul Journal of Health Care Law}{DePaul J. Health Care L.}
\hi@abbrev{DePaul Law Review}{DePaul L. Rev.}
\hi@abbrev{DePaul-LCA Journal of Art and Entertainment Law and Policy}{DePaul-LCA J. Art \& Ent. L. \& Pol'y}
\hi@abbrev{Delaware Journal of Corporate Law}{Del. J. Corp. L.}
\hi@abbrev{Denver Journal of International Law and Policy}{Denv. J. Int'l L. \& Pol'y}
\hi@abbrev{Denver University Law Review}{Denv. U. L. Rev.}
\hi@abbrev{Department of State Bulletin}{Dep't St. Bull.}
\hi@abbrev{Dickinson Journal of Environmental Law and Policy}{Dick. J. Envtl. L. \& Pol'y}
\hi@abbrev{Dickinson Journal of International Law}{Dick. J. Int'l L.}
\hi@abbrev{Dickinson Law Review}{Dick. L. Rev.}
\hi@abbrev{The Digest: The National Italian-American Bar Association Law Journal}{Digest}
\hi@abbrev{District of Columbia Law Review}{D.C. L. Rev.}
\hi@abbrev{Drake Journal of Agricultural Law}{Drake J. Agric. L.}
\hi@abbrev{Drake Law Review}{Drake L. Rev.}
\hi@abbrev{Duke Environmental Law and Policy Forum}{Duke Envtl. L. \& Pol'y F.}
\hi@abbrev{Duke Journal of Comparative and International Law}{Duke J. Comp. \& Int'l L.}
\hi@abbrev{Duke Journal of Gender Law and Policy}{Duke J. Gender L. \& Pol'y}
\hi@abbrev{Duke Law Journal}{Duke L.J.}
\hi@abbrev{Duquesne Business Law Journal}{Duq. Bus. L.J.}
\hi@abbrev{Duquesne Law Review}{Duq. L. Rev.}
\hi@abbrev{Ecology Law Quarterly}{Ecology L.Q.}
\hi@abbrev{Elder Law Journal}{Elder L.J.}
\hi@abbrev{Elder's Advisor: The Journal of Elder Law and Post-Retirement Planning}{Elder's Advisor}
\hi@abbrev{Emory International Law Review}{Emory Int'l L. Rev.}
\hi@abbrev{Emory Law Journal}{Emory L.J.}
\hi@abbrev{Employee Rights and Employment Policy Journal}{Emp. Rts. \& Emp. Pol'y J.}
\hi@abbrev{Energy Law Journal}{Energy L.J.}
\hi@abbrev{Environmental Law}{Envtl. L.}
\hi@abbrev{Environmental Lawyer}{Envtl. Law.}
\hi@abbrev{Family and Conciliation Courts Review}{Fam. \& Conciliation Cts. Rev.}
\hi@abbrev{Family Court Review}{Fam. Ct. Rev.}
\hi@abbrev{Family Law Quarterly}{Fam. L.Q.}
\hi@abbrev{Federal Circuit Bar Journal}{Fed. Cir. B.J.}
\hi@abbrev{Federal Rules Decisions}{F.R.D.}
\hi@abbrev{Federal Communications Law Journal}{Fed. Comm. L.J.}
\hi@abbrev{Federal Probation}{Fed. Probation}
\hi@abbrev{Federal Sentencing Reporter}{Fed. Sent'g Rep.}
\hi@abbrev{Florida Journal of International Law}{Fla. J. Int'l L.}
\hi@abbrev{Florida Law Review}{Fla. L. Rev.}
\hi@abbrev{Florida State Journal of Transnational Law and Policy}{Fla. St. J. Transnat'l L. \& Pol'y}
\hi@abbrev{Florida State University Law Review}{Fla. St. U. L. Rev.}
\hi@abbrev{Florida Tax Review}{Fla. Tax Rev.}
\hi@abbrev{Food and Drug Law Journal}{Food \& Drug L.J.}
\hi@abbrev{Food Drug Cosmetic Law Journal}{Food Drug Cosm. L.J.}
\hi@abbrev{Fordham Environmental Law Review}{Fordham Envtl. L. Rev.}
\hi@abbrev{Fordham Intellectual Property, Media and Entertainment Law Journal}{Fordham Intell. Prop. Media \& Ent. L.J.}
\hi@abbrev{Fordham International Law Journal}{Fordham Int'l L.J.}
\hi@abbrev{Fordham Journal of Corporate and Financial Law}{Fordham J. Corp. \& Fin. L.}
\hi@abbrev{Fordham Law Review}{Fordham L. Rev.}
\hi@abbrev{Fordham Urban Law Journal}{Fordham Urb. L.J.}
\hi@abbrev{Foreign Broadcast Information Service}{F.B.I.S.}
\hi@abbrev{The Forum}{Forum}
\hi@abbrev{Franchise Law Journal}{Franchise L.J.}
\hi@abbrev{George Mason Law Review}{Geo. Mason L. Rev.}
\hi@abbrev{George Mason University Civil Rights Law Journal}{Geo. Mason U. Civ. Rts. L.J.}
\hi@abbrev{George Washington International Law Review}{Geo. Wash. Int'l L. Rev.}
\hi@abbrev{George Washington Journal of International Law and Economics}{Geo. Wash. J. Int'l L. \& Econ.}
\hi@abbrev{George Washington Law Review}{Geo. Wash. L. Rev.}
\hi@abbrev{Georgetown Immigration Law Journal}{Geo. Immigr. L.J.}
\hi@abbrev{Georgetown International Environmental Law Review}{Geo. Int'l Envtl. L. Rev.}
\hi@abbrev{The Georgetown Journal of Gender and the Law}{Geo. J. Gender \& L.}
\hi@abbrev{Georgetown Journal of International Law}{Geo. J. Int'l L.}
\hi@abbrev{Georgetown Journal of Legal Ethics}{Geo. J. Legal Ethics}
\hi@abbrev{Georgetown Journal on Poverty Law and Policy}{Geo. J. on Poverty L. \& Pol'y}
\hi@abbrev{Georgetown Law Journal}{Geo. L.J.}
\hi@abbrev{Georgia Journal of International and Comparative Law}{Ga. J. Int'l \& Comp. L.}
\hi@abbrev{Georgia Law Review}{Ga. L. Rev.}
\hi@abbrev{Georgia State University Law Review}{Ga. St. U. L. Rev.}
\hi@abbrev{Glendale Law Review}{Glendale L. Rev.}
\hi@abbrev{Golden Gate University Law Review}{Golden Gate U. L. Rev.}
\hi@abbrev{Gonzaga Law Review}{Gonz. L. Rev.}
\hi@abbrev{Great Plains Natural Resources Journal}{Great Plains Nat. Resources J.}
\hi@abbrev{Green Bag}{Green Bag}
\hi@abbrev{Guild Practitioner}{Guild Prac.}
\hi@abbrev{Hamline Journal of Public Law and Policy}{Hamline J. Pub. L. \& Pol'y}
\hi@abbrev{Hamline Law Review}{Hamline L. Rev.}
\hi@abbrev{Harvard BlackLetter Law Journal}{Harv. BlackLetter L.J.}
\hi@abbrev{Harvard Civil Rights-Civil Liberties Law Review}{Harv. C.R.-C.L. L. Rev.}
\hi@abbrev{Harvard Environmental Law Review}{Harv. Envtl. L. Rev.}
\hi@abbrev{Harvard International Law Journal}{Harv. Int'l L.J.}
\hi@abbrev{Harvard Journal of Law and Public Policy}{Harv. J.L. \& Pub. Pol'y}
\hi@abbrev{Harvard Journal of Law and Technology}{Harv. J.L. \& Tech.}
\hi@abbrev{Harvard Journal on Legislation}{Harv. J. on Legis.}
\hi@abbrev{Harvard Law Review}{Harv. L. Rev.}
\hi@abbrev{Harvard Negotiation Law Review}{Harv. Negot. L. Rev.}
\hi@abbrev{Harvard Women's Law Journal}{Harv. Women's L.J.}
\hi@abbrev{Hastings Communications and Entertainment Law Journal}{Hastings Comm. \& Ent. L.J.}
\hi@abbrev{Hastings Constitutional Law Quarterly}{Hastings Const. L.Q.}
\hi@abbrev{Hastings International and Comparative Law Review}{Hastings Int'l \& Comp. L. Rev.}
\hi@abbrev{Hastings Law Journal}{Hastings L.J.}
\hi@abbrev{Hastings West-Northwest Journal of Environmental Law and Policy}{Hastings W.-Nw. J. Envtl. L. \& Pol'y}
\hi@abbrev{Hastings Women's Law Journal}{Hastings Women's L.J.}
\hi@abbrev{Health Matrix}{Health Matrix}
\hi@abbrev{High Technology Law Journal}{High Tech. L.J.}
\hi@abbrev{Hofstra Labor and Employment Law Journal}{Hofstra Lab. \& Emp. L.J.}
\hi@abbrev{Hofstra Law Review}{Hofstra L. Rev.}
\hi@abbrev{Hofstra Property Law Journal}{Hofstra Prop. L.J.}
\hi@abbrev{Houston Journal of International Law}{Hous. J. Int'l L.}
\hi@abbrev{Houston Law Review}{Hous. L. Rev.}
\hi@abbrev{Howard Law Journal}{Howard L.J.}
\hi@abbrev{Human Rights Quarterly}{Hum. Rts. Q.}
\hi@abbrev{Idaho Law Review}{Idaho L. Rev.}
\hi@abbrev{IDEA: The Journal of Law and Technology}{IDEA}
\hi@abbrev{Illinois Bar Journal}{Ill. B.J.}
\hi@abbrev{ILSA Journal of International and Comparative Law}{ILSA J. Int'l \& Comp. L.}
\hi@abbrev{Immigration and Nationality Law Review}{Immigr. \& Nat'lity L. Rev.}
\hi@abbrev{In the Public Interest}{In Pub. Interest}
\hi@abbrev{Indiana International and Comparative Law Review}{Ind. Int'l \& Comp. L. Rev.}
\hi@abbrev{Indiana Law Journal}{Ind. L.J.}
\hi@abbrev{Indiana Law Review}{Ind. L. Rev.}
\hi@abbrev{Industrial and Labor Relations Review}{Indus. \& Lab. Rel. Rev.}
\hi@abbrev{Institute on Estate Planning}{Inst. on Est. Plan.}
\hi@abbrev{Institute on Federal Taxation}{Inst. on Fed. Tax'n}
\hi@abbrev{Institute on Oil and Gas Law and Taxation}{Inst. on Oil \& Gas L. \& Tax'n}
\hi@abbrev{Institute on Planning, Zoning, and Eminent Domain}{Inst. on Plan. Zoning \& Eminent Domain}
\hi@abbrev{Institute on Private Investments and Investors Abroad}{Inst. on Priv. Inv. \& Inv. Abroad}
\hi@abbrev{Institute on Securities Regulation}{Inst. on Sec. Reg.}
\hi@abbrev{International and Comparative Law Quarterly}{Int'l \& Comp. L.Q.}
\hi@abbrev{International Journal of Law and Psychiatry}{Int'l J.L. \& Psychiatry}
\hi@abbrev{International Lawyer}{Int'l Law.}
\hi@abbrev{International Legal Perspectives}{Int'l Legal Persp.}
\hi@abbrev{International Organization}{Int'l Org.}
\hi@abbrev{International Organization Law Review}{Int'l Org. L. Rev.}
\hi@abbrev{International Review of Law and Economics}{Int'l Rev. L. \& Econ.}
\hi@abbrev{Iowa Law Review}{Iowa L. Rev.}
\hi@abbrev{JAG Journal}{JAG J.}
\hi@abbrev{John Marshall Journal of Computer and Information Law}{J. Marshall J. Computer \& Info. L.}
\hi@abbrev{John Marshall Law Review}{J. Marshall L. Rev.}
\hi@abbrev{Journal of Agricultural Law}{J. Agric. L.}
\hi@abbrev{Journal of Air Law and Commerce}{J. Air L. \& Com.}
\hi@abbrev{Journal of Appellate Practice and Process}{J. App. Prac. \& Process}
\hi@abbrev{Journal of Business Law}{J. Bus. L.}
\hi@abbrev{Journal of Chinese Law}{J. Chinese L.}
\hi@abbrev{Journal of College and University Law}{J.C. \& U.L.}
\hi@abbrev{Journal of Contemporary Health Law and Policy}{J. Contemp. Health L. \& Pol'y}
\hi@abbrev{Journal of Contemporary Law}{J. Contemp. L.}
\hi@abbrev{Journal of Contemporary Legal Issues}{J. Contemp. Legal Issues}
\hi@abbrev{Journal of Corporation Law}{J. Corp. L.}
\hi@abbrev{Journal of Criminal Law and Criminology}{J. Crim. L. \& Criminology}
\hi@abbrev{Journal of Dispute Resolution}{J. Disp. Resol.}
\hi@abbrev{Journal of Energy Law and Policy}{J. Energy L. \& Pol'y}
\hi@abbrev{Journal of Energy, Natural Resources and Environmental Law}{J. Energy Nat. Resources \& Envtl. L.}
\hi@abbrev{Journal of Environmental Law and Litigation}{J. Envtl. L. \& Litig.}
\hi@abbrev{Journal of Family Law}{J. Fam. L.}
\hi@abbrev{Journal of Gender, Race and Justice}{J. Gender Race \& Just.}
\hi@abbrev{Journal of Health and Hospital Law}{J. Health \& Hosp. L.}
\hi@abbrev{Journal of Health Care Law and Policy}{J. Health Care L. \& Pol'y}
\hi@abbrev{Journal of Health Politics, Policy and Law}{J. Health Pol. Pol'y \& L.}
\hi@abbrev{Journal of Health Law}{J. Health L.}
\hi@abbrev{Journal of Intellectual Property}{J. Intell. Prop.}
\hi@abbrev{Journal of Intellectual Property Law}{J. Intell. Prop. L.}
\hi@abbrev{Journal of International Arbitration}{J. Int'l Arb.}
\hi@abbrev{Journal of International Legal Studies}{J. Int'l Legal Stud.}
\hi@abbrev{Journal of International Wildlife Law and Policy}{J. Int'l Wildlife L. \& Pol'y}
\hi@abbrev{Journal of Land, Resources and Environmental Law}{J. Land Resources \& Envtl. L.}
\hi@abbrev{Journal of Land Use and Environmental Law}{J. Land Use \& Envtl. L.}
\hi@abbrev{Journal of Law and Commerce}{J.L. \& Com.}
\hi@abbrev{Journal of Law and Economics}{J.L. \& Econ.}
\hi@abbrev{Journal of Law and Education}{J.L. \& Educ.}
\hi@abbrev{Journal of Law and Health}{J.L. \& Health}
\hi@abbrev{Journal of Law and Policy}{J.L. \& Pol'y}
\hi@abbrev{Journal of Law and Politics}{J.L. \& Pol.}
\hi@abbrev{Journal of Law, Economics and Organization}{J.L. Econ. \& Org.}
\hi@abbrev{Journal of Law in Society}{J.L. Soc'y}
\hi@abbrev{Journal of Law, Medicine and Ethics}{J.L. Med. \& Ethics}
\hi@abbrev{Journal of Legal Education}{J. Legal Educ.}
\hi@abbrev{Journal of Legal Medicine}{J. Legal Med.}
\hi@abbrev{Journal of Legal Studies}{J. Legal Stud.}
\hi@abbrev{Journal of Legislation}{J. Legis.}
\hi@abbrev{Journal of Maritime Law and Commerce}{J. Mar. L. \& Com.}
\hi@abbrev{Journal of Medicine and Law}{J. Med. \& L.}
\hi@abbrev{Journal of Mineral Law and Policy}{J. Min. L. \& Pol'y}
\hi@abbrev{Journal of Products Liability}{J. Prod. Liab.}
\hi@abbrev{Journal of Science and Technology Law}{J. Sci. \& Tech. L.}
\hi@abbrev{Journal of Small and Emerging Business Law}{J. Small \& Emerging Bus. L.}
\hi@abbrev{Journal of Southern Legal History}{J. S. Legal Hist.}
\hi@abbrev{Journal of Technology Law and Policy}{J. Tech. L. \& Pol'y}
\hi@abbrev{Journal of the American Academy of Matrimonial Lawyers}{J. Am. Acad. Matrim. Law.}
\hi@abbrev{Journal of the American Medical Association}{JAMA}
\hi@abbrev{Journal of the Legal Profession}{J. Legal Prof.}
\hi@abbrev{Journal of the Patent and Trademark Office Society}{J. Pat. \& Trademark Off. Soc'y}
\hi@abbrev{Journal of the Suffolk Academy of Law}{J. Suffolk Acad. L.}
\hi@abbrev{Juridical Review}{Jurid. Rev.}
\hi@abbrev{Jurimetrics: The Journal of Law, Science and Technology}{Jurimetrics J.}
\hi@abbrev{Juris Doctor}{Juris Dr.}
\hi@abbrev{Juris Magazine}{Juris Mag.}
\hi@abbrev{Justice System Journal}{Just. Sys. J.}
\hi@abbrev{Kansas Journal of Law and Public Policy}{Kan. J.L. \& Pub. Pol'y}
\hi@abbrev{Kentucky Law Journal}{Ky. L.J.}
\hi@abbrev{Labor Law Journal}{Lab. L.J.}
\hi@abbrev{Labor Lawyer}{Lab. Law.}
\hi@abbrev{Land and Water Law Review}{Land \& Water L. Rev.}
\hi@abbrev{La Raza Law Journal}{La Raza L.J.}
\hi@abbrev{Law and Contemporary Problems}{Law \& Contemp. Probs.}
\hi@abbrev{Law and History Review}{Law \& Hist. Rev.}
\hi@abbrev{Law and Human Behavior}{Law \& Hum. Behav.}
\hi@abbrev{Law and Inequality}{Law \& Ineq.}
\hi@abbrev{Law and Policy in International Business}{Law \& Pol'y Int'l Bus.}
\hi@abbrev{Law and Psychology Review}{Law \& Psychol. Rev.}
\hi@abbrev{Law and Social Inquiry}{Law \& Soc. Inquiry}
\hi@abbrev{Law and Society Review}{Law \& Soc'y Rev.}
\hi@abbrev{Law Library Journal}{Law Libr. J.}
\hi@abbrev{Lawyer's Reports Annotated}{L.R.A.}
\hi@abbrev{Lewis and Clark Law Review}{Lewis \& Clark L. Rev.}
\hi@abbrev{Lincoln Law Review}{Lincoln L. Rev.}
\hi@abbrev{Louisiana Law Review}{La. L. Rev.}
\hi@abbrev{Loyola Law Review (New Orleans)}{Loy. L. Rev.}
\hi@abbrev{Loyola of Los Angeles Entertainment Law Review}{Loy. L.A. Ent. L. Rev.}
\hi@abbrev{Loyola of Los Angeles International and Comparative Law Review}{Loy. L.A. Int'l \& Comp. L. Rev.}
\hi@abbrev{Loyola of Los Angeles Law Review}{Loy. L.A. L. Rev.}
\hi@abbrev{Loyola University of Chicago Law Journal}{Loy. U. Chi. L.J.}
\hi@abbrev{Maine Law Review}{Me. L. Rev.}
\hi@abbrev{Major Tax Planning}{Major Tax Plan.}
\hi@abbrev{Marquette Intellectual Property Law Review}{Marq. Intell. Prop. L. Rev.}
\hi@abbrev{Marquette Law Review}{Marq. L. Rev.}
\hi@abbrev{Marquette Sports Law Journal}{Marq. Sports L.J.}
\hi@abbrev{Maryland Journal of Contemporary Legal Issues}{Md. J. Contemp. Legal Issues}
\hi@abbrev{Maryland Journal of International Law and Trade}{Md. J. Int'l L. \& Trade}
\hi@abbrev{Maryland Law Review}{Md. L. Rev.}
\hi@abbrev{Massachusetts Law Review}{Mass. L. Rev.}
\hi@abbrev{McGeorge Law Review}{McGeorge L. Rev.}
\hi@abbrev{McGill Law Journal}{McGill L.J.}
\hi@abbrev{Melbourne University Law Review}{Melb. U. L. Rev.}
\hi@abbrev{Mercer Law Review}{Mercer L. Rev.}
\hi@abbrev{Michigan Business Law Journal}{Mich. Bus. L.J.}
\hi@abbrev{Michigan Journal of Gender and Law}{Mich. J. Gender \& L.}
\hi@abbrev{Michigan Journal of International Law}{Mich. J. Int'l L.}
\hi@abbrev{Michigan Journal of Race and Law}{Mich. J. Race \& L.}
\hi@abbrev{Michigan Law Review}{Mich. L. Rev.}
\hi@abbrev{Michigan Telecommunications and Technology Law Review}{Mich. Telecomm. \& Tech. L. Rev.}
\hi@abbrev{Military Law Review}{Mil. L. Rev.}
\hi@abbrev{Minnesota Intellectual Property Review}{Minn. Intell. Prop. Rev.}
\hi@abbrev{Minnesota Journal of Global Trade}{Minn. J. Global Trade}
\hi@abbrev{Minnesota Law Review}{Minn. L. Rev.}
\hi@abbrev{Mississippi College Law Review}{Miss. C. L. Rev.}
\hi@abbrev{Mississippi Law Journal}{Miss. L.J.}
\hi@abbrev{Missouri Environmental Law and Policy Review}{Mo. Envtl. L. \& Pol'y Rev.}
\hi@abbrev{Missouri Law Review}{Mo. L. Rev.}
\hi@abbrev{Modern Law Review}{Mod. L. Rev.}
\hi@abbrev{Monash University Law Review}{Monash U. L. Rev.}
\hi@abbrev{Montana Law Review}{Mont. L. Rev.}
\hi@abbrev{Monthly Labor Review}{Monthly Lab. Rev.}
\hi@abbrev{National Black Law Journal}{Nat'l Black L.J.}
\hi@abbrev{Natural Resources Journal}{Nat. Resources J.}
\hi@abbrev{Nebraska Law Review}{Neb. L. Rev.}
\hi@abbrev{New England International and Comparative Law Annual}{New Eng. Int'l \& Comp. L. Ann.}
\hi@abbrev{New England Journal of Medicine}{New Eng. J. Med.}
\hi@abbrev{New England Journal on Criminal and Civil Confinement}{New Eng. J. on Crim. \& Civ. Confinement}
\hi@abbrev{New Law Journal}{New L.J.}
\hi@abbrev{New Mexico Law Review}{N.M. L. Rev.}
\hi@abbrev{New York City Law Review}{N.Y. City L. Rev.}
\hi@abbrev{New York International Law Review}{N.Y. Int'l L. Rev.}
\hi@abbrev{New York Law School Journal of Human Rights}{N.Y.L. Sch. J. Hum. Rts.}
\hi@abbrev{New York Law School Journal of International and Comparative Law}{N.Y.L. Sch. J. Int'l \& Comp. L.}
\hi@abbrev{New York Law School Law Review}{N.Y.L. Sch. L. Rev.}
\hi@abbrev{New York State Bar Association Antitrust Law Symposium}{N.Y. St. B.A. Antitrust L. Symp.}
\hi@abbrev{New York University Environmental Law Journal}{N.Y.U. Envtl. L.J.}
\hi@abbrev{New York University Journal of International Law and Politics}{N.Y.U. J. Int'l L. \& Pol.}
\hi@abbrev{New York University Journal of Legislation and Public Policy}{N.Y.U. J. Legis. \& Pub. Pol'y}
\hi@abbrev{New York University Law Review}{N.Y.U. L. Rev.}
\hi@abbrev{New York University Review of Law and Social Change}{N.Y.U. Rev. L. \& Soc. Change}
\hi@abbrev{New York University School of Law Moot Court Casebook}{N.Y.U. Moot Ct. Casebook}
\hi@abbrev{NEXUS: A Journal of Opinion}{NEXUS}
\hi@abbrev{North Carolina Banking Institute}{N.C. Banking Inst.}
\hi@abbrev{North Carolina Central Law Journal}{N.C. Cent. L.J.}
\hi@abbrev{North Carolina Journal of International Law and Commercial Regulation}{N.C. J. Int'l L. \& Com. Reg.}
\hi@abbrev{North Carolina Law Review}{N.C. L. Rev.}
\hi@abbrev{North Dakota Law Review}{N.D. L. Rev.}
\hi@abbrev{Northern Illinois University Law Review}{N. Ill. U. L. Rev.}
\hi@abbrev{Northern Kentucky Law Review}{N. Ky. L. Rev.}
\hi@abbrev{Northwestern Journal of International Law and Business}{Nw. J. Int'l L. \& Bus.}
\hi@abbrev{Northwestern University Law Review}{Nw. U. L. Rev.}
\hi@abbrev{Nota Bene}{Nota Bene}
\hi@abbrev{Notre Dame Journal of Law, Ethics and Public Policy}{Notre Dame J.L. Ethics \& Pub. Pol'y}
\hi@abbrev{Notre Dame Law Review}{Notre Dame L. Rev.}
\hi@abbrev{Nova Law Review}{Nova L. Rev.}
\hi@abbrev{Ocean and Coastal Law Journal}{Ocean \& Coastal L.J.}
\hi@abbrev{Ohio Northern University Law Review}{Ohio N.U. L. Rev.}
\hi@abbrev{Ohio State Journal on Dispute Resolution}{Ohio St. J. on Disp. Resol.}
\hi@abbrev{Ohio State Law Journal}{Ohio St. L.J.}
\hi@abbrev{Oil and Gas Tax Quarterly}{Oil \& Gas Tax Q.}
\hi@abbrev{Oklahoma City University Law Review}{Okla. City U. L. Rev.}
\hi@abbrev{Oklahoma Law Review}{Okla. L. Rev.}
\hi@abbrev{Oregon Law Review}{Or. L. Rev.}
\hi@abbrev{Osgoode Hall Law Journal}{Osgoode Hall L.J.}
\hi@abbrev{Otago Law Review}{Otago L. Rev.}
\hi@abbrev{Ottawa Law Review}{Ottawa L. Rev.}
\hi@abbrev{Pace Environmental Law Review}{Pace Envtl. L. Rev.}
\hi@abbrev{Pace Law Review}{Pace L. Rev.}
\hi@abbrev{Pacific Law Journal}{Pac. L.J.}
\hi@abbrev{Pacific Rim Law and Policy Journal}{Pac. Rim L. \& Pol'y J.}
\hi@abbrev{Patent Law Annual}{Pat. L. Ann.}
\hi@abbrev{Pepperdine Law Review}{Pepp. L. Rev.}
\hi@abbrev{Performing Arts Review}{Perf. Arts Rev.}
\hi@abbrev{Potomac Law Review}{Potomac L. Rev.}
\hi@abbrev{Practical Lawyer}{Prac. Law.}
\hi@abbrev{Preventive Law Reporter}{Preventive L. Rep.}
\hi@abbrev{Preview of United States Supreme Court Cases}{Preview U.S. Sup. Ct. Cas.}
\hi@abbrev{Probate Law Journal (National College of Probate Judges and Boston University School of Law)}{Prob. L.J.}
\hi@abbrev{Public Interest Law Reporter}{Pub. Int. L. Rep.}
\hi@abbrev{Public Land Law Review}{Pub. Land L. Rev.}
\hi@abbrev{Public Land and Resources Law Review}{Pub. Land \& Resources L. Rev.}
\hi@abbrev{Publishing, Entertainment, Advertising and Allied Fields Law Quarterly}{Pub. Ent. Advert. \& Allied Fields L.Q.}
\hi@abbrev{Quinnipiac Health Law Journal}{Quinnipiac Health L.J.}
\hi@abbrev{Quinnipiac Law Review}{Quinnipiac L. Rev.}
\hi@abbrev{Quinnipiac Probate Law Journal}{Quinnipiac Prob. L.J.}
\hi@abbrev{Race and Ethnic Ancestry Law Journal}{Race \& Ethnic Anc. L.J.}
\hi@abbrev{Real Property, Probate and Trust Journal}{Real Prop. Prob. \& Tr. J.}
\hi@abbrev{Regent University Law Review}{Regent U. L. Rev.}
\hi@abbrev{Review of Litigation}{Rev. Litig.}
\hi@abbrev{Revista de Derecho Puertorriqueno}{Rev. Der. P.R.}
\hi@abbrev{Revista Juridica Universidad de Puerto Rico}{Rev. Jur. U.P.R.}
\hi@abbrev{Richmond Journal of Global Law and Business}{Rich. J. Global L. \& Bus.}
\hi@abbrev{Richmond Journal of Law and the Public Interest}{Rich. J.L. \& Pub. Int.}
\hi@abbrev{Richmond Journal of Law and Technology}{Rich. J.L. \& Tech.}
\hi@abbrev{RISK: Health, Safety and Environment}{RISK}
\hi@abbrev{Rocky Mountain Mineral Law Institute}{Rocky Mtn. Min. L. Inst.}
\hi@abbrev{Roger Williams University Law Review}{Roger Williams U. L. Rev.}
\hi@abbrev{Rutgers-Camden Law Journal}{Rutgers-Cam. L.J.}
\hi@abbrev{Rutgers Computer and Technology Law Journal}{Rutgers Computer \& Tech. L.J.}
\hi@abbrev{Rutgers Law Journal}{Rutgers L.J.}
\hi@abbrev{Rutgers Law Record}{Rutgers L. Rec.}
\hi@abbrev{Rutgers Law Review}{Rutgers L. Rev.}
\hi@abbrev{Rutgers Race and the Law Review}{Rutgers Race \& L. Rev.}
\hi@abbrev{St. John's Journal of Legal Commentary}{St. John's J. Legal Comment.}
\hi@abbrev{St. John's Law Review}{St. John's L. Rev.}
\hi@abbrev{Saint Louis University Law Journal}{St. Louis U. L.J.}
\hi@abbrev{Saint Louis University Public Law Review}{St. Louis U. Pub. L. Rev.}
\hi@abbrev{Saint Louis-Warsaw Transatlantic Law Journal}{St. Louis-Warsaw Transatlantic L.J.}
\hi@abbrev{St. Mary's Law Journal}{St. Mary's L.J.}
\hi@abbrev{St. Thomas Law Review}{St. Thomas L. Rev.}
\hi@abbrev{San Diego Law Review}{San Diego L. Rev.}
\hi@abbrev{San Fernando Valley Law Review}{San Fern. V. L. Rev.}
\hi@abbrev{Santa Clara Computer and High Technology Law Journal}{Santa Clara Computer \& High Tech. L.J.}
\hi@abbrev{Santa Clara Law Review}{Santa Clara L. Rev.}
\hi@abbrev{The Scholar: St. Mary's Law Review on Minority Issues}{Scholar}
\hi@abbrev{Scientific American}{Sci. Am.}
\hi@abbrev{Seattle University Law Review}{Seattle U. L. Rev.}
\hi@abbrev{Seton Hall Constitutional Law Journal}{Seton Hall Const. L.J.}
\hi@abbrev{Seton Hall Journal of Sport Law}{Seton Hall J. Sport L.}
\hi@abbrev{Seton Hall Law Review}{Seton Hall L. Rev.}
\hi@abbrev{Seton Hall Legislative Journal}{Seton Hall Legis. J.}
\hi@abbrev{Social Service Review}{Soc. Serv. Rev.}
\hi@abbrev{Software Law Journal}{Software L.J.}
\hi@abbrev{South Carolina Environmental Law Journal}{S.C. Envtl. L.J.}
\hi@abbrev{South Carolina Law Review}{S.C. L. Rev.}
\hi@abbrev{South Dakota Law Review}{S.D. L. Rev.}
\hi@abbrev{South Texas Law Review}{S. Tex. L. Rev.}
\hi@abbrev{Southern California Interdisciplinary Law Journal}{S. Cal. Interdisc. L.J.}
\hi@abbrev{Southern California Law Review}{S. Cal. L. Rev.}
\hi@abbrev{Southern California Review of Law and Women's Studies}{S. Cal. Rev. L. \& Women's Stud.}
\hi@abbrev{Southern Illinois University Law Journal}{S. Ill. U. L.J.}
\hi@abbrev{Southern Methodist University Law Review}{SMU L. Rev.}
\hi@abbrev{Southern University Law Review}{S.U. L. Rev.}
\hi@abbrev{Southwestern Journal of Law and Trade in the Americas}{Sw. J.L. \& Trade Am.}
\hi@abbrev{Southwestern Law Journal}{Sw. L.J.}
\hi@abbrev{Southwestern University Law Review}{Sw. U. L. Rev.}
\hi@abbrev{Sports Lawyers Journal}{Sports Law. J.}
\hi@abbrev{Stanford Environmental Law Journal}{Stan. Envtl. L.J.}
\hi@abbrev{Stanford Journal of International Law}{Stan. J. Int'l L.}
\hi@abbrev{Stanford Law and Policy Review}{Stan. L. \& Pol'y Rev.}
\hi@abbrev{Stanford Law Review}{Stan. L. Rev.}
\hi@abbrev{State Bar of Texas Environmental Law Journal}{St. B. Tex. Envtl. L.J.}
\hi@abbrev{Stetson Law Forum}{Stetson L.F.}
\hi@abbrev{Stetson Law Review}{Stetson L. Rev.}
\hi@abbrev{Suffolk Journal of Trial and Appellate Advocacy}{Suffolk J. Trial \& App. Advoc.}
\hi@abbrev{Suffolk Transnational Law Review}{Suffolk Transnat'l L. Rev.}
\hi@abbrev{Suffolk University Law Review}{Suffolk U. L. Rev.}
\hi@abbrev{Supreme Court Review}{Sup. Ct. Rev.}
\hi@abbrev{Sydney Law Review}{Sydney L. Rev.}
\hi@abbrev{Syracuse Journal of International Law and Commerce}{Syracuse J. Int'l L. \& Com.}
\hi@abbrev{Syracuse Law Review}{Syracuse L. Rev.}
\hi@abbrev{Tax Adviser}{Tax Adviser}
\hi@abbrev{Tax Law Review}{Tax L. Rev.}
\hi@abbrev{Tax Lawyer}{Tax Law.}
\hi@abbrev{Tax Management International Journal}{Tax Mgmt. Int'l J.}
\hi@abbrev{Tax Notes}{Tax Notes}
\hi@abbrev{Taxes---The Tax Magazine}{Taxes}
\hi@abbrev{Temple Environmental Law and Technology Journal}{Temp. Envtl. L. \& Tech. J.}
\hi@abbrev{Temple International and Comparative Law Journal}{Temp. Int'l \& Comp. L.J.}
\hi@abbrev{Temple Law Review}{Temp. L. Rev.}
\hi@abbrev{Temple Political and Civil Rights Law Review}{Temp. Pol. \& Civ. Rts. L. Rev.}
\hi@abbrev{Tennessee Journal of Practice and Procedure}{Tenn. J. Prac. \& Proc.}
\hi@abbrev{Tennessee Law Review}{Tenn. L. Rev.}
\hi@abbrev{Texas Forum on Civil Liberties and Civil Rights}{Tex. F. on C.L. \& C.R.}
\hi@abbrev{Texas Hispanic Journal of Law and Policy}{Tex. Hisp. J.L. \& Pol'y}
\hi@abbrev{Texas Intellectual Property Law Journal}{Tex. Intell. Prop. L.J.}
\hi@abbrev{Texas International Law Journal}{Tex. Int'l L.J.}
\hi@abbrev{Texas Journal of Business Law}{Tex. J. Bus. L.}
\hi@abbrev{Texas Journal of Women and the Law}{Tex. J. Women \& L.}
\hi@abbrev{Texas Law Review}{Tex. L. Rev.}
\hi@abbrev{Texas Review of Law and Politics}{Tex. Rev. L. \& Pol.}
\hi@abbrev{Texas Tech Law Review}{Tex. Tech L. Rev.}
\hi@abbrev{Texas Wesleyan Law Review}{Tex. Wesleyan L. Rev.}
\hi@abbrev{Third World Legal Studies}{Third World Legal Stud.}
\hi@abbrev{Thomas Jefferson Law Review}{T. Jefferson L. Rev.}
\hi@abbrev{Thomas M. Cooley Journal of Practical and Clinical Law}{T.M. Cooley J. Prac. \& Clinical L.}
\hi@abbrev{Thomas M. Cooley Law Review}{T.M. Cooley L. Rev.}
\hi@abbrev{Thurgood Marshall Law Review}{T. Marshall L. Rev.}
\hi@abbrev{Toledo Journal of Great Lakes' Law, Science and Policy}{Tol. J. Great Lakes' L. Sci. \& Pol'y}
\hi@abbrev{Touro Journal of Transnational Law}{Touro J. Transnat'l L.}
\hi@abbrev{Touro Law Review}{Touro L. Rev.}
\hi@abbrev{Trademark Reporter}{Trademark Rep.}
\hi@abbrev{Transnational Law and Contemporary Problems}{Transnat'l L. \& Contemp. Probs.}
\hi@abbrev{The Transnational Lawyer}{Transnat'l Law.}
\hi@abbrev{Transportation Law Journal}{Transp. L.J.}
\hi@abbrev{Transportation Practitioners Journal}{Transp. Prac. J.}
\hi@abbrev{Trial Lawyer's Guide}{Trial Law. Guide}
\hi@abbrev{Tulane Environmental Law Journal}{Tul. Envtl. L.J.}
\hi@abbrev{Tulane European and Civil Law Forum}{Tul. Eur. \& Civ. L.F.}
\hi@abbrev{Tulane Journal of International and Comparative Law}{Tul. J. Int'l \& Comp. L.}
\hi@abbrev{Tulane Journal of Law and Sexuality}{Tul. J.L. \& Sexuality}
\hi@abbrev{Tulane Law Review}{Tul. L. Rev.}
\hi@abbrev{Tulane Maritime Law Journal}{Tul. Mar. L.J.}
\hi@abbrev{Tulsa Journal of Comparative and International Law}{Tulsa J. Comp. \& Int'l L.}
\hi@abbrev{Tulsa Law Journal}{Tulsa L.J.}
\hi@abbrev{UCLA Bulletin of Law and Technology}{UCLA Bull. L. \& Tech.}
\hi@abbrev{UCLA Entertainment Law Review}{UCLA Ent. L. Rev.}
\hi@abbrev{UCLA Journal of Environmental Law and Policy}{UCLA J. Envtl. L. \& Pol'y}
\hi@abbrev{UCLA Journal of International Law and Foreign Affairs}{UCLA J. Int'l L. \& Foreign Aff.}
\hi@abbrev{UCLA Law Review}{UCLA L. Rev.}
\hi@abbrev{UCLA Pacific Basin Law Journal}{UCLA Pac. Basin L.J.}
\hi@abbrev{UCLA Women's Law Journal}{UCLA Women's L.J.}
\hi@abbrev{UMKC Law Review}{UMKC L. Rev.}
\hi@abbrev{UN Monthly Chronicle}{UN Monthly Chron.}
\hi@abbrev{Uniform Commercial Code Law Journal}{UCC L.J.}
\hi@abbrev{Uniform Commercial Code Reporter-Digest}{UCC Rep.-Dig.}
\hi@abbrev{United States-Mexico Law Journal}{U.S.-Mex. L.J.}
\hi@abbrev{University of Arkansas at Little Rock Law Review}{U. Ark. Little Rock L. Rev.}
\hi@abbrev{University of Baltimore Intellectual Property Law Journal}{U. Balt. Intell. Prop. L.J.}
\hi@abbrev{University of Baltimore Journal of Environmental Law}{U. Balt. J. Envtl. L.}
\hi@abbrev{University of Baltimore Law Forum}{U. Balt. L.F.}
\hi@abbrev{University of Baltimore Law Review}{U. Balt. L. Rev.}
\hi@abbrev{University of California at Davis Law Review}{U.C. Davis L. Rev.}
\hi@abbrev{University of Chicago Law Review}{U. Chi. L. Rev.}
\hi@abbrev{University of Chicago Legal Forum}{U. Chi. Legal F.}
\hi@abbrev{University of Cincinnati Law Review}{U. Cin. L. Rev.}
\hi@abbrev{University of Colorado Law Review}{U. Colo. L. Rev.}
\hi@abbrev{University of Dayton Law Review}{U. Dayton L. Rev.}
\hi@abbrev{University of Denver Water Law Review}{U. Denv. Water L. Rev.}
\hi@abbrev{University of Detroit Mercy Law Review}{U. Det. Mercy L. Rev.}
\hi@abbrev{University of the District of Columbia David Clarke School of Law Law Review}{UDC/DCSL L. Rev.}
\hi@abbrev{University of Florida Journal of Law and Public Policy}{U. Fla. J.L. \& Pub. Pol'y}
\hi@abbrev{University of Florida Law Review}{U. Fla. L. Rev.}
\hi@abbrev{University of Hawaii Law Review}{U. Haw. L. Rev.}
\hi@abbrev{University of Illinois Journal of Law, Technology and Policy}{U. Ill. J.L. Tech. \& Pol'y}
\hi@abbrev{University of Illinois Law Review}{U. Ill. L. Rev.}
\hi@abbrev{University of Kansas Law Review}{U. Kan. L. Rev.}
\hi@abbrev{University of Memphis Law Review}{U. Mem. L. Rev.}
\hi@abbrev{University of Miami Business Law Review}{U. Miami Bus. L. Rev.}
\hi@abbrev{University of Miami Entertainment and Sports Law Review}{U. Miami Ent. \& Sports L. Rev.}
\hi@abbrev{University of Miami Inter-American Law Review}{U. Miami Inter-Am. L. Rev.}
\hi@abbrev{University of Miami Law Review}{U. Miami L. Rev.}
\hi@abbrev{University of Miami Yearbook of International Law}{U. Miami Y.B. Int'l L.}
\hi@abbrev{University of Michigan Journal of Law Reform}{U. Mich. J.L. Reform}
\hi@abbrev{University of Pennsylvania Journal of Constitutional Law}{U. Pa. J. Const. L.}
\hi@abbrev{University of Pennsylvania Journal of International Economic Law}{U. Pa. J. Int'l Econ. L.}
\hi@abbrev{University of Pennsylvania Journal of Labor and Employment Law}{U. Pa. J. Lab. \& Emp. L.}
\hi@abbrev{University of Pennsylvania Law Review}{U. Pa. L. Rev.}
\hi@abbrev{University of Pittsburgh Law Review}{U. Pitt. L. Rev.}
\hi@abbrev{University of Puget Sound Law Review}{U. Puget Sound L. Rev.}
\hi@abbrev{University of Richmond Law Review}{U. Rich. L. Rev.}
\hi@abbrev{University of San Francisco Law Review}{U.S.F. L. Rev.}
\hi@abbrev{University of San Francisco Maritime Law Journal}{U.S.F. Mar. L.J.}
\hi@abbrev{University of Seattle Law Review}{U. Seattle L. Rev.}
\hi@abbrev{University of Toledo Law Review}{U. Tol. L. Rev.}
\hi@abbrev{University of Toronto Faculty of Law Review}{U. Toronto Fac. L. Rev.}
\hi@abbrev{University of Toronto Law Journal}{U. Toronto L.J.}
\hi@abbrev{University of West Los Angeles Law Review}{UWLA L. Rev.}
\hi@abbrev{Urban Lawyer}{Urb. Law.}
\hi@abbrev{Utah Law Review}{Utah L. Rev.}
\hi@abbrev{Valparaiso University Law Review}{Val. U. L. Rev.}
\hi@abbrev{Vanderbilt Journal of Entertainment Law and Practice}{Vand. J. Ent. L. \& Prac.}
\hi@abbrev{Vanderbilt Journal of Transnational Law}{Vand. J. Transnat'l L.}
\hi@abbrev{Vanderbilt Law Review}{Vand. L. Rev.}
\hi@abbrev{Vermont Law Review}{Vt. L. Rev.}
\hi@abbrev{Villanova Environmental Law Journal}{Vill. Envtl. L.J.}
\hi@abbrev{Villanova Law Review}{Vill. L. Rev.}
\hi@abbrev{Villanova Sports and Entertainment Law Journal}{Vill. Sports \& Ent. L.J.}
\hi@abbrev{Virginia Environmental Law Journal}{Va. Envtl. L.J.}
\hi@abbrev{Virginia Journal of International Law}{Va. J. Int'l L.}
\hi@abbrev{Virginia Journal of Law and Technology}{Va. J.L. \& Tech.}
\hi@abbrev{Virginia Journal of Social Policy and the Law}{Va. J. Soc. Pol'y \& L.}
\hi@abbrev{Virginia Journal of Sports and the Law}{Va. J. Sports \& L.}
\hi@abbrev{Virginia Law Review}{Va. L. Rev.}
\hi@abbrev{Virginia Tax Review}{Va. Tax Rev.}
\hi@abbrev{Wake Forest Law Review}{Wake Forest L. Rev.}
\hi@abbrev{Wall Street Journal}{Wall St. J.}
\hi@abbrev{Washburn Law Journal}{Washburn L.J.}
\hi@abbrev{Washington and Lee Law Review}{Wash. \& Lee L. Rev.}
\hi@abbrev{Washington Law Review}{Wash. L. Rev.}
\hi@abbrev{Washington Monthly}{Wash. Monthly}
\hi@abbrev{Washington University Journal of Law and Policy}{Wash. U. J.L. \& Pol'y}
\hi@abbrev{Washington University Journal of Urban and Contemporary Law}{Wash. U. J. Urb. \& Contemp. L.}
\hi@abbrev{Washington University Law Quarterly}{Wash. U. L.Q.}
\hi@abbrev{Wayne Law Review}{Wayne L. Rev.}
\hi@abbrev{West Virginia Law Review}{W. Va. L. Rev.}
\hi@abbrev{Western New England Law Review}{W. New Eng. L. Rev.}
\hi@abbrev{Western State University Law Review}{W. St. U. L. Rev.}
\hi@abbrev{Whittier Law Review}{Whittier L. Rev.}
\hi@abbrev{Widener Journal of Public Law}{Widener J. Pub. L.}
\hi@abbrev{Widener Law Symposium Journal}{Widener L. Symp. J.}
\hi@abbrev{Willamette Law Review}{Willamette L. Rev.}
\hi@abbrev{William and Mary Bill of Rights Journal}{Wm. \& Mary Bill Rts. J.}
\hi@abbrev{William and Mary Journal of Women and the Law}{Wm. \& Mary J. Women \& L.}
\hi@abbrev{William and Mary Law Review}{Wm. \& Mary L. Rev.}
\hi@abbrev{William Mitchell Law Review}{Wm. Mitchell L. Rev.}
\hi@abbrev{Wisconsin Environmental Law Journal}{Wis. Envtl. L.J.}
\hi@abbrev{Wisconsin International Law Journal}{Wis. Int'l L.J.}
\hi@abbrev{Wisconsin Law Review}{Wis. L. Rev.}
\hi@abbrev{Wisconsin Women's Law Journal}{Wis. Women's L.J.}
\hi@abbrev{Women's Rights Law Reporter}{Women's Rts. L. Rep.}
\hi@abbrev{Yale Human Rights and Development Law Journal}{Yale Hum. Rts. \& Dev. L.J.}
\hi@abbrev{Yale Journal of International Law}{Yale J. Int'l L.}
\hi@abbrev{Yale Journal of Law and Feminism}{Yale J.L. \& Feminism}
\hi@abbrev{Yale Journal of Law and the Humanities}{Yale J.L. \& Human.}
\hi@abbrev{Yale Journal of World Public Order}{Yale J. World Pub. Ord.}
\hi@abbrev{Yale Journal on Regulation}{Yale J. on Reg.}
\hi@abbrev{Yale Law and Policy Review}{Yale L. \& Pol'y Rev.}
\hi@abbrev{Yale Law Journal}{Yale L.J.}
%
%
\endinput
